---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-",
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)
```

# pmtiles: Create PMTiles with Tippecanoe in R

<!-- badges: start -->
[![R-CMD-check](https://github.com/nptscot/pmtiles/workflows/R-CMD-check/badge.svg)](https://github.com/nptscot/pmtiles/actions)
[![R-CMD-check](https://github.com/nptscot/pmtiles/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nptscot/pmtiles/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `pmtiles` package provides a simple interface to create PMTiles using the Tippecanoe command-line tool. PMTiles is a file format for efficiently storing map tiles as a single file.

## Installation

You can install the development version of pmtiles from GitHub with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("nptscot/pmtiles")
```

### Prerequisites

This package requires [Tippecanoe](https://github.com/felt/tippecanoe) to be installed on your system. Please follow the installation instructions on the Tippecanoe GitHub page.

You can check if Tippecanoe is installed and get its version:

```{r}
library(pmtiles)
```

Alternatively, you can load the package with the following for local development:

```{r, eval=FALSE}
devtools::load_all()
```

```{r, eval=FALSE}
# Check if Tippecanoe is installed
is_tippecanoe_installed()
```

## Quick Start

The simplest way to create PMTiles is to use the `pmtiles()` function, after loading the package:

```{r, eval=FALSE}
# Create PMTiles from a GeoJSON file
pmtiles("your_file.geojson")

# Create PMTiles from a GeoPackage file
pmtiles("your_file.gpkg")

# Create PMTiles from an sf object
pmtiles(rnet_sf)
```

This will create a PMTiles file in the `./pmtiles` directory with sensible defaults.

## Working with the Included Dataset

To create PMTiles from this dataset:

```{r, eval=FALSE}
pmtiles(
  input_file = edinburgh_centre,
  output_name = "edinburgh_example",
  attribution = "City of Edinburgh | pmtiles R package"
)
```

## Advanced Usage

For more control over the PMTiles creation process, use the `create_pmtiles()` function:

```{r, eval=FALSE}
# Create PMTiles with custom parameters
create_pmtiles(
  input_file = "your_file.geojson",
  output_folder = "output",
  output_name = "my_tiles",
  layer_name = "my_layer",
  attribution = "My Organization",
  min_zoom = 6,
  max_zoom = 13,
  drop_smallest = TRUE,
  max_tile_bytes = 2000000,
  buffer = 5,
  simplification = 10,
  force = TRUE
)
```

## License

This project is licensed under the MIT License. 
