---
title: "Introduction to pmtiles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pmtiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pmtiles)
```

## Introduction

The `pmtiles` package provides a simple interface to create PMTiles using the Tippecanoe command-line tool. PMTiles is a file format for efficiently storing map tiles as a single file.

## Prerequisites

Before using this package, you need to have Tippecanoe installed on your system. You can check if Tippecanoe is installed with:

```{r}
is_tippecanoe_installed()
```

If Tippecanoe is installed, you can check its version:

```{r}
get_tippecanoe_version()
```

If Tippecanoe is not installed, please follow the installation instructions at: [https://github.com/felt/tippecanoe](https://github.com/felt/tippecanoe).

## Creating PMTiles

### Quick Start

The simplest way to create PMTiles is to use the `pmtiles()` function:

```{r, eval=FALSE}
# Create PMTiles from a GeoJSON file
pmtiles("path/to/your/data.geojson")
```

This will create a PMTiles file in the `./pmtiles` directory with sensible defaults.

### Advanced Usage

For more control over the PMTiles creation process, use the `create_pmtiles()` function:

```{r, eval=FALSE}
# Create PMTiles with custom parameters
create_pmtiles(
  input_file = "path/to/your/data.geojson",
  output_folder = "output/directory",
  output_name = "my_tiles",
  layer_name = "my_layer",
  attribution = "My Organization",
  min_zoom = 6,
  max_zoom = 13,
  drop_smallest = TRUE,
  max_tile_bytes = 2000000,
  buffer = 5,
  simplification = 10,
  force = TRUE
)
```

## Parameter Details

The main function `create_pmtiles()` accepts the following parameters:

- `input_file`: Path to the input GeoJSON file
- `output_folder`: Path to the output folder
- `output_name`: Name of the output file (without extension)
- `layer_name`: Name of the layer
- `attribution`: Attribution text
- `min_zoom`: Minimum zoom level (default: 6)
- `max_zoom`: Maximum zoom level (default: 13)
- `drop_smallest`: Whether to drop smallest features as needed (default: TRUE)
- `max_tile_bytes`: Maximum tile size in bytes (default: 2000000)
- `buffer`: Buffer size in pixels (default: 5)
- `simplification`: Simplification factor (default: NULL)
- `force`: Whether to overwrite existing files (default: TRUE)
- `extra_args`: Additional arguments to pass to Tippecanoe (default: NULL)

## Example Workflow

Here's a complete example workflow:

```{r, eval=FALSE}
library(pmtiles)

# Check if Tippecanoe is installed
if (is_tippecanoe_installed()) {
  # Create PMTiles from a GeoJSON file
  create_pmtiles(
    input_file = "my_data.geojson",
    output_folder = "output",
    output_name = "my_tiles",
    attribution = "My Organization",
    min_zoom = 6,
    max_zoom = 15
  )
} else {
  message("Tippecanoe is not installed. Please install it first.")
}
``` 